A Study on Online Sequential Learning using Bandits

### 2017-12-13 Chapter6/contribution.tex
Latest on 13/12/2017

In this chapter, we propose an actively adaptive upper confidence bound (UCB) algorithm, referred to as Improved Changepoint Detector (ImpCPD), that tries to locate the chnagepoints in the distribution and adapt accordingly to minimize the cumulative regret. Our solution to the piecewise stochastic problem also depends on restarting where we employ ImpCPD which tries to minimize the cumulative regret by balancing exploration-exploitation and a changepoint detector which tries to predict a changepoint with high probability. When the changepoint is detected ImpCPD is again restarted with all the past history of actions and rewards erased. For the changepoint detection we propose a novel algorithm CPDI which works as a subroutine in conjunction with the main ImpCPD algorithm.

>>>>

In this chapter, we propose an actively adaptive upper confidence bound (UCB) algorithm, referred to as Improved Changepoint Detector (ImpCPD), that tries to locate the changepoints in the distribution and adapt accordingly to minimize the cumulative regret. Our solution to the piecewise stochastic problem also depends on restarting where we employ ImpCPD which tries to minimize the cumulative regret by balancing exploration-exploitation and a changepoint detector which tries to predict a changepoint with high probability. When the changepoint is detected ImpCPD is again restarted with all the past history of actions and rewards erased. For the changepoint detection we propose a novel algorithm CPDI which works as a subroutine in conjunction with the main ImpCPD algorithm.

### 2017-12-13 Chapter6/mainresult.tex
Latest on 11/12/2017
Latest on 13/12/2017

\begin{theorem}
\label{psbandit:Theorem:1}
The expected cumulative regret of ImpCPD algorithm is upper bounded by,
\begin{align*}
\E[R_t] &\leq \sum_{i = 1}^K\sum_{j=1}^{G}\bigg[ 1 
%%%%%%%%%%
+ \dfrac{4T^{\frac{3}{2}}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}}
%%%%%%%%%%
+ \Delta^{opt}_{i,c_j} + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
& + \dfrac{2T^{\frac{3}{2}}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
&+ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}
\bigg]
\end{align*}

where $\alpha,\psi$ are exploration parameters and $\Delta^{opt}_{i,c_{G+1}} = 0,\forall i\in\A$.
\end{theorem}

@@

\textbf{Step 0.(Vital Assumption for proving):} In this proof, we assume that all the changepoints are detected by the algorithm.

\textbf{Step 1.(Define some notations):} In this proof, we define the confidence interval for the $i$-th arm as $s_i=\sqrt{\dfrac{\alpha\log(\psi T\epsilon_m^2)}{n_{i}}}$. The phase numbers are denoted by $m=0,1,\ldots,M$ where $M=\frac{1}{2}\log_{2}\frac{T}{e}$. For the sake of brevity, in this proof we write $n_i$ instead of $n_{i,t_0:t_p}$ denoting only the number of times the arm $i$ is pulled between two restarts, ie, between $t_0$ to $t_p$.

\textbf{Step 2.(Define an optimality stopping phase $m_{i,c_j}$):} We define an optimality stopping phase $m_{i,c_j}$ for a sub-optimal arm $i\in\A$ as the first phase after which the arm $i$ is no longer pulled till the $c_j$-th changepoint is detected such that,

\begin{align*}
m_{i,c_j} = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{opt}_{i,c_j}}{4} \right\rbrace
\end{align*}

\textbf{Step 3.(Define a changepoint stopping phase $p_{i,c_j}$):} We define a changepoint stopping phase $p_{i,c_j}$ for an arm $i\in\A$ such that it is the first phase when the changepoint $c_j$ is detected such that,

\begin{align*}
p_{i,c_j} = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{chg}_{i,c_j}}{4} \right\rbrace
\end{align*}

@@

Also, in the $m_{i,c_j}$-th phase if $n_i \geq \ell_{m_{i,c_j}} = \dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\epsilon_{m_{i,c_j}}}$ then we can show that,
\begin{align*}
s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\ell_{m_{i,c_j}}}} \leq \sqrt{\alpha\epsilon_{m_{i,c_j}}\dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{\log(\psi T\epsilon_{m_{i,c_j}}^2)}} \leq \dfrac{\Delta^{opt}_{i,c_j}}{4}.
\end{align*}

@@

\begin{align*}
\hat{r}_{i,c_j} + s_i \leq {r}_{i,c_j} + 4s_i - 2s_i \leq {r}_{i,c_j} + \Delta^{opt}_{i,c_j} - 2s_i \leq {r}_{i*,c_j} - 2s_{i*} \leq \hat{r}_{i*,c_j} - s_{i*}
\end{align*}

@@

\begin{align*}
\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace.
\end{align*}

But the event $\hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_i$ is possible only when the following three events occur, $\hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} , \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i$ and $r_{i*}-r_{i} < 2s_i $. But the third event will not happen for $n_i\geq \ell_{m_{i,c_j}}$. Proceeding as before, we can show that the probability of the remaining two events is bounded by,

\begin{align*}
&\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
&\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\left( \Pb\lbrace \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i \rbrace \bigcup \Pb\lbrace \hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} \rbrace \right)\leq 2\left(\dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\right)\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha + 1}}.
\end{align*}

@@

\begin{align*}
\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace r_{i,c_j} + s_i > r_{i*,c_j} + s_{i*} \rbrace \leq \dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
\end{align*}

@@

\begin{align*}
\dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha +1}} &\leq \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{M}\left(\dfrac{1}{\epsilon_{m}}\right)^{2\alpha +1} \overset{(a)}{\leq} \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\left(\dfrac{2(2^M - 1)}{2 - 1}\right)^{2\alpha +1} \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\overset{(b)}{\leq} \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\left(\sqrt{T}\right)^{2\alpha +1} = \dfrac{4\sqrt{T}\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi)^{\alpha}}.
\end{align*}

Here, in $(a)$ we use the standard geometric progression formula and in $(b)$ we substitute the value of $M=\dfrac{1}{2}\log_{2}\dfrac{T}{e}$. Bounding this trivially by $T\Delta^{opt}_{i,c_j}$ for each arm $i\in\A$ we get the regret suffered for arm $i$ after the $m_{i,c_j}$-th phase  as,

\begin{align*}
\sum_{i\in\A}\left( \dfrac{4T\Delta^{opt}_{i,c_j}\sqrt{T}\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi)^{\alpha}} \right) \leq \sum_{i\in\A}\left( \dfrac{4T^{\frac{3}{2}}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}} \right).
\end{align*}

@@

\begin{align*}
s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2\ell_{p_{i,c_j}}}} \leq \sqrt{\alpha\epsilon_{p_{i,c_j}}\dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{\log(\psi T\epsilon_{p_{i,c_j}}^2)}} \leq \dfrac{\Delta^{chg}_{i,c_j}}{4}.
\end{align*}

@@

\begin{align*}
\hat{r}_{i,c_{j-1}} + s_{i} \leq {r}_{i,c_{j-1}} + 4s_{i} - 2s_{i} \leq {r}_{i,c_{j-1}} + \Delta^{chg}_{i,c_j} -2s_{i} \leq {r}_{i,c_{j}} - 2s_i \leq \hat{r}_{i,c_{j}} - s_i.
\end{align*}

@@

\begin{align*}
\sum_{m=0}^{p_{i,c_j}}\sum_{n_i=\ell_{p_{i-1}}}^{\ell_{p_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} \leq  r_{i,c_j} - s_i \rbrace &\leq \sum_{m=0}^{p_{i,c_j}}\sum_{n_i=\ell_{p_{i-1, c_j}}}^{\ell_{p_{i,c_j}}}\exp\left(-2s_i^2n_i \right) \leq \dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}.
\end{align*}

Hence, the probability that the changepoint is not detected by the first event in equation \ref{eq:arm-pull-chg} is bounded by,
\begin{align*}
\dfrac{\log(\psi T)}{(\psi T \epsilon_{p_{i,c_j}}^2)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}.
\end{align*}

@@

\begin{align*}
\dfrac{2\log(\psi T)}{(\psi T\epsilon_{p_{i,c_j}}^2)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}} \overset{(a)}{\leq} \dfrac{2\sqrt{T}\log(\psi T \epsilon_{p_{i,c_j}}^2)}{(\psi)^{\alpha}} .
\end{align*}

Here, in $(a)$ we follow the same steps as in \textbf{step 4} to reduce the expression to the above form. Furthermore, bounding the regret trivially (after the changepoint $c_j$) by $\Delta^{opt}_{i,c_{j+1}}$ for each arm $i\in\A$, we get

\begin{align*}
\sum_{i\in\A}\left( \dfrac{2T\Delta^{opt}_{i,c_{j+1}}\sqrt{T}\log(\psi T \epsilon_{p_{i,c_j}}^2)}{(\psi)^{\alpha}} \right) \leq \sum_{i\in\A}\left( \dfrac{2T^{\frac{3}{2}}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}} \right).
\end{align*}

@@

\begin{align*}
\E[R_{T}]&= \sum_{i = 1}^K\sum_{j=1}^{G}\Delta^{opt}_{i,c_j}\E[n_{i_{t',c_j}\neq i^*_{t',c_j},\forall t'=t_{c_{j-1}}:t_{c_j}}] \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
& \leq \sum_{i = 1}^K\sum_{j=1}^{G}\bigg[ 1 
%%%%%%%%%%
+ \underbrace{ \dfrac{4T^{\frac{3}{2}}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{from Step 4}}
%%%%%%%%%%
+ \underbrace{\Delta^{opt}_{i,c_j} + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})}}_{\textbf{from Step 5}}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
& + \underbrace{ \dfrac{2T^{\frac{3}{2}}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{from Step 6}}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
&+ \underbrace{ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}}_{\textbf{from Step 7}}
\bigg]
\end{align*}

>>>>

\begin{theorem}
\label{psbandit:Theorem:1}
The expected cumulative regret of ImpCPD algorithm is upper bounded by,
\begin{align*}
\E[R_t] &\leq \sum_{i = 1}^K\sum_{j=1}^{G}\bigg[ 1 
%%%%%%%%%%
+ \dfrac{4T^{\frac{3}{2}}C_{\gamma}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}}
%%%%%%%%%%
+ \Delta^{opt}_{i,c_j} + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
& + \dfrac{2T^{\frac{3}{2}}C_{\gamma}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
&+ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}
\bigg]
\end{align*}

where $\alpha,\psi,\gamma$ are exploration parameters, $C_{\gamma}=\left( \dfrac{1+\gamma}{\gamma}\right)$ and $\Delta^{opt}_{i,c_{G+1}} = 0,\forall i\in\A$.
\end{theorem}

@@

\textbf{Step 0.(Vital Assumption for proving):} In this proof, we assume that all the changepoints are detected by the algorithm with some delay. Since, all the gaps are significant (Assumption \ref{assm:chg-gap}) and there is sufficient delay between two changepoints (Assumption \ref{assm:space-gap}), we can take this assumption for proving the result.

\textbf{Step 1.(Define some notations):} In this proof, we define the confidence interval for the $i$-th arm as $s_i=\sqrt{\dfrac{\alpha\log(\psi T\epsilon_m^2)}{n_{i}}}$. The phase numbers are denoted by $m=0,1,\ldots,M$ where $M=\frac{1}{2}\log_{1+\gamma}\frac{T}{e}$. For the sake of brevity, in this proof we write $n_i$ instead of $n_{i,t_0:t_p}$ denoting the number of times the arm $i$ is pulled between two restarts, ie, between $t_0$ to $t_p$ (as shown in algorithm). For each sub-optimal arm $i$, we consider their contribution to cumulative regret individually till each of the changepoint

\textbf{Step 2.(Define an optimality stopping phase $m_{i,c_j}$):} We define an optimality stopping phase $m_{i,c_j}$ for a sub-optimal arm $i\in\A$ as the first phase after which the arm $i$ is no longer pulled till the $c_j$-th changepoint is detected such that for $\gamma>0$,

\begin{align*}
m_{i,c_j} = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{opt}_{i,c_j}}{(1+\gamma)^2} \right\rbrace
\end{align*}

\textbf{Step 3.(Define a changepoint stopping phase $p_{i,c_j}$):} We define a changepoint stopping phase $p_{i,c_j}$ for an arm $i\in\A$ such that it is the first phase when the changepoint $c_j$ is detected such that for $\gamma > 0$,

\begin{align*}
p_{i,c_j} = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{chg}_{i,c_j}}{(1+\gamma)^2} \right\rbrace
\end{align*}

@@

Also, in the $m_{i,c_j}$-th phase if $n_i \geq \ell_{m_{i,c_j}} = \dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\epsilon_{m_{i,c_j}}}$ then we can show that,
\begin{align*}
s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\ell_{m_{i,c_j}}}} \leq \sqrt{\alpha\epsilon_{m_{i,c_j}}\dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{\log(\psi T\epsilon_{m_{i,c_j}}^2)}} \leq \dfrac{\Delta^{opt}_{i,c_j}}{(1+\gamma)^2}.
\end{align*}

@@

\begin{align*}
\hat{r}_{i,c_j} + s_i \leq {r}_{i,c_j} + (1+\gamma)^2 s_i - (1+\gamma)s_i \leq {r}_{i,c_j} + \Delta^{opt}_{i,c_j} - (1+\gamma)s_i \leq {r}_{i*,c_j} - (1+\gamma)s_{i*} \leq \hat{r}_{i*,c_j} - s_{i*}
\end{align*}

@@

\begin{align*}
\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace.
\end{align*}

But the event $\hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_i$ is possible only when the following three events occur, $\hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} , \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i$ and $r_{i*}-r_{i} < (1+\gamma)^2 s_i $. But the third event will not happen for $n_i\geq \ell_{m_{i,c_j}}$. Proceeding as before, we can show that the probability of the remaining two events is bounded by,

\begin{align*}
&\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
& \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\left( \Pb\lbrace \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i \rbrace \bigcup \Pb\lbrace \hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} \rbrace \right)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\left( \Pb\lbrace \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i \rbrace \right) +  \sum_{m=0}^{m_{i,c_j}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\left( \Pb\lbrace \hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} \rbrace \right) \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\dfrac{1}{\psi T\epsilon_{m_{i,c_j}}^2} +  \sum_{m=0}^{m_{i,c_j}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\dfrac{1}{\psi T\epsilon_{m_{i,c_j}}^2} \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq 2\left(\dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\right)\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha + 1}}.
\end{align*}

@@

\begin{align*}
\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace &\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace r_{i,c_j} + s_i > r_{i*,c_j} + s_{i*} \rbrace\\
%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq \dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
\end{align*}

@@

\begin{align*}
\dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha +1}} &\leq \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{M}\left(\dfrac{1}{\epsilon_{m}}\right)^{2\alpha +1}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%
& \overset{(a)}{\leq} \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\left(\dfrac{(1+\gamma)((1+\gamma)^M - 1)}{(1+\gamma) - 1}\right)^{2\alpha +1} \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\overset{(b)}{\leq} \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\left( \left( \dfrac{1+\gamma}{\gamma}\right) \sqrt{T}\right)^{2\alpha +1} \overset{(c)}{=} \dfrac{4\sqrt{T}\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi)^{\alpha}}.
\end{align*}

Here, in $(a)$ we use the standard geometric progression formula, in $(b)$ we substitute the value of $M=\dfrac{1}{2}\log_{1+\gamma}\dfrac{T}{e}$ and in $(c)$ we substitute $C_{\gamma}= \left( \dfrac{1+\gamma}{\gamma}\right)$ . Bounding this trivially by $T\Delta^{opt}_{i,c_j}$ for each arm $i\in\A$ we get the regret suffered for arm $i$ after the $m_{i,c_j}$-th phase  as,

\begin{align*}
\sum_{i\in\A}\left( \dfrac{4T\Delta^{opt}_{i,c_j}\sqrt{T}C_{\gamma}\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi)^{\alpha}} \right) \leq \sum_{i\in\A}\left( \dfrac{4T^{\frac{3}{2}}C_{\gamma}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}} \right).
\end{align*}

@@

\begin{align*}
s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2\ell_{p_{i,c_j}}}} \leq \sqrt{\alpha\epsilon_{p_{i,c_j}}\dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{\log(\psi T\epsilon_{p_{i,c_j}}^2)}} \leq \dfrac{\Delta^{chg}_{i,c_j}}{(1+\gamma)^2}.
\end{align*}

@@

\begin{align*}
\hat{r}_{i,c_{j-1}} + s_{i} \leq {r}_{i,c_{j-1}} + (1+\gamma)^2 s_{i} - (1+\gamma)s_{i} \leq {r}_{i,c_{j-1}} + \Delta^{chg}_{i,c_j} - (1+\gamma)s_{i} \leq {r}_{i,c_{j}} - (1+\gamma)s_i \leq \hat{r}_{i,c_{j}} - s_i.
\end{align*}

@@

\begin{align*}
\sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} \leq  r_{i,c_j} - s_i \rbrace &\leq \sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\exp\left(-2s_i^2n_i \right) \leq \dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}.
\end{align*}

%\ell_{p_{i-1, c_j}}
Hence, the probability that the changepoint is not detected by the first event in equation \ref{eq:arm-pull-chg} is bounded by,
\begin{align*}
\dfrac{\log(\psi T)}{(\psi T \epsilon_{p_{i,c_j}}^2)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}.
\end{align*}

@@

\begin{align*}
\dfrac{2\log(\psi T)}{(\psi T\epsilon_{p_{i,c_j}}^2)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}} \overset{(a)}{\leq} \dfrac{2C_{\gamma}\sqrt{T}\log(\psi T \epsilon_{p_{i,c_j}}^2)}{(\psi)^{\alpha}} .
\end{align*}

Here, in $(a)$ we substitute $C_{\gamma}=\left( \dfrac{1+\gamma}{\gamma}\right)$ and we follow the same steps as in \textbf{step 4} to reduce the expression to the above form. Furthermore, bounding the regret trivially (after the changepoint $c_j$) by $\Delta^{opt}_{i,c_{j+1}}$ for each arm $i\in\A$, we get

\begin{align*}
\sum_{i\in\A}\left( \dfrac{2T\Delta^{opt}_{i,c_{j+1}}\sqrt{T}C_{\gamma}\log(\psi T \epsilon_{p_{i,c_j}}^2)}{(\psi)^{\alpha}} \right) \leq \sum_{i\in\A}\left( \dfrac{2T^{\frac{3}{2}}C_{\gamma}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}} \right).
\end{align*}

@@

\begin{align*}
\E[R_{T}]&= \sum_{i = 1}^K\sum_{j=1}^{G}\Delta^{opt}_{i,c_j}\E[n_{i_{t',c_j}\neq i^*_{t',c_j},\forall t'=t_{c_{j-1}}:t_{c_j}}] \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
& \leq \sum_{i = 1}^K\sum_{j=1}^{G}\bigg[ 1 
%%%%%%%%%%
+ \underbrace{ \dfrac{4T^{\frac{3}{2}}C_{\gamma}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{from Step 4}}
%%%%%%%%%%
+ \underbrace{\Delta^{opt}_{i,c_j} + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})}}_{\textbf{from Step 5}}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
& + \underbrace{ \dfrac{2T^{\frac{3}{2}}C_{\gamma}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{from Step 6}}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
&+ \underbrace{ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}}_{\textbf{from Step 7}}
\bigg]
\end{align*}
